### 2015-08-10 rscripts/data_review.Rmd
updates

>>>>

Looking at day-of-week, week-of-year patterns:

```{r, echo=F}
byweekday.dt <- censor.dt[,
  .N,
  keyby=list(location_id, weekday)
]
loctotals <- byweekday.dt[,list(total=sum(N)), keyby=location_id]
weekday.kmeans.src <- byweekday.dt[loctotals][,list(distribution=N/total), keyby=list(location_id, weekday)]
kmByWeekDayData <- kmParse2(weekday.kmeans.src, 10, 5, "location_id", "weekday")
ggplot(weekday.kmeans.src[kmByWeekDayData$clustering]) +
  theme_bw() + facet_grid(. ~ cluster, scales="free") +
  aes(x=factor(location_id), y=weekday, fill=log(distribution)) +
  geom_raster() +
  scale_x_discrete("location_id", labels="")

byweek.dt <- censor.dt[,
  .N,
  keyby=list(location_id, week)
]
week.kmeans.src <- byweek.dt[
  byweek.dt[,list(total=sum(N)), keyby=location_id]
][,
  list(distribution=N/total), keyby=list(location_id, week)
]
kmByWeekData <- kmParse2(week.kmeans.src, 10, 5, "location_id", "week")
ggplot(week.kmeans.src[kmByWeekData$clustering]) +
  theme_bw() + facet_grid(. ~ cluster, scales="free") +
  aes(x=factor(location_id), y=week, fill=log(distribution)) +
  geom_raster() +
  scale_x_discrete("location_id", labels="")

bymonth.dt <- censor.dt[,
  .N,
  keyby=list(location_id, month)
]
month.kmeans.src <- bymonth.dt[
  bymonth.dt[,list(total=sum(N)), keyby=location_id]
][,
  list(distribution=N/total), keyby=list(location_id, month)
]
kmBymonthData <- kmParse2(month.kmeans.src, 10, 5, "location_id", "month")
ggplot(month.kmeans.src[kmBymonthData$clustering]) +
  theme_bw() + facet_grid(. ~ cluster, scales="free") +
  aes(x=factor(location_id), y=month, fill=log(distribution)) +
  geom_raster() +
  scale_x_discrete("location_id", labels="")
